### 2021-02-19 paper.tex
Add more features and namespace table.

%===========[ PREAMBLE ]========================================================
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a4paper, top=0.98in, bottom=0.79in, left=0.98in, right=0.98in]{geometry}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{todonotes}
\usepackage{csquotes}
\usepackage{siunitx}
\usepackage[labelsep=period]{caption}
\usepackage{mwe}
\usepackage{xfrac}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{cleveref}
\usepackage{aurl}
\daurl{bb}{http://www.snik.eu/ontology/bb/}
\daurl{ob}{http://www.snik.eu/ontology/bb/}
\daurl{meta}{http://www.snik.eu/ontology/meta/}
\graphicspath{{./img/}}
%\usepackage[backend=biber, style=ieee]{biblatex} %For bibliography management with biblatex
%\addbibresource{/path/to/bib/file/example.bib} %Change path to your own .bib file

@@

% version 3.18.0
\label{sec:relatedwork}
\section*{Related Work}
Different techniques of Linked Data visualization are motivated and described in \cite{linkeddatavisualization}, including graph-based visualization.

@@

\emph{OSMoSys} is an experimental prototype of a web application using the Sigma.js graph drawing library.
It and handles large graphs using a level-of-detail system.
However, the demo is not accessible anymore and the code is not freely available.
Thus the maximum graph size and performance cannot be determined.

@@

\subsection*{Role Use}
\todo{describe role use here}
\cref{fig:classuse}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{class-use-project-manager.pdf}
    \caption{\emph{Role Use} of \aurl{bb}{ProjectManager}. Outermost layer ommitted due to space limitiations.}\label{fig:classuse}
\end{figure}

@@

\subsection*{Mixed Operations}
\subsubsection*{Spiderworm}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\linewidth]{spiderworm.pdf}
    \caption{\emph{Spiderworm} between \aurl{bb}{PatientIdentificationNumber} and \aurl{bb}{QualityOfData}.}
	\label{fig:path}
\end{figure}
\vspace{-3pt}

@@

\begin{table}[h!]
    \centering
    \caption{Table captions should be placed above the tables.}\label{tab:<table-name>}
    \begin{tabularx}{\linewidth}{|X|X|}
        \hline
        \textbf{Hazard Class}    & \textbf{A 1 to A III}                            \\ \hline
        Flash point              & $< 21 ^\circ C / > 55 ^\circ C$                  \\ \hline
        Density at $15 ^\circ C$ & $720\ \sfrac{kg}{m^3}$ to $860\ \sfrac{kg}{m^3}$ \\ \hline
        Kinematic Viscosity      & $0,65$ to $4,0\cdot 10–6\ \sfrac{m^2}{s}$        \\ \hline
    \end{tabularx}
\end{table}

@@

\begin{itemize}
    \item Bullet points may be used
    \item ...
\end{itemize}

@@

\section*{Acknowledgement}
This work is supported by the DFG (German Research Foundation) under the Project SNIK, Grant no. 1605/7-1 and 1387/8-1. SNIK Graph was presented in poster form at \cite{snikgraphposter}.
\section*{References}

>>>>

%===========[ PREAMBLE ]========================================================
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a4paper, top=0.98in, bottom=0.79in, left=0.98in, right=0.98in]{geometry}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{todonotes}
\usepackage{csquotes}
\usepackage{listings}
\lstset{language=SPARQL,breaklines=true}
\usepackage{siunitx}
\usepackage[labelsep=period]{caption}
\usepackage{mwe}
\usepackage{xfrac}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{cleveref}
\usepackage{aurl}
\daurl{bb}{http://www.snik.eu/ontology/bb/}
\daurl{ob}{http://www.snik.eu/ontology/bb/}
\daurl{meta}{http://www.snik.eu/ontology/meta/}
\graphicspath{{./img/}}
%\usepackage[backend=biber, style=ieee]{biblatex} %For bibliography management with biblatex
%\addbibresource{/path/to/bib/file/example.bib} %Change path to your own .bib file

@@

% version 3.18.0
\label{sec:relatedwork}
\section*{Related Work}
\todo{thomas, please finish this section, does not need to be long. Or remove the section and only cite the book? or include it in the respective parts?}
Different techniques of Linked Data visualization are motivated and described in \cite{linkeddatavisualization}, including graph-based visualization.

@@

\todo{kh: i think osmosys is not so relevant}
\emph{OSMoSys} is an experimental prototype of a web application using the Sigma.js graph drawing library.
It and handles large graphs using a level-of-detail system.
However, the demo is not accessible anymore and the code is not freely available.
Thus the maximum graph size and performance cannot be determined.

@@

\subsection*{Role Use}
\begin{figure}[h]
\begin{lstlisting}
SELECT DISTINCT ?inner ?middle ?outer ?outerx {
 <role> (rdfs:subClassOf|skos:closeMatch|^skos:closeMatch)* ?inner.
 ?inner meta:subTopClass meta:Role.
 OPTIONAL {
  ?inner ?p ?middle.
  ?middle meta:subTopClass meta:Function.
  OPTIONAL {
   ?middle ?q ?outer.
   ?outer meta:subTopClass meta:EntityType.
   OPTIONAL {?outer (skos:closeMatch|^skos:closeMatch|^rdfs:subClassOf)+ ?outerx.}
}}}
\end{lstlisting}
\caption{SPARQL query to generate the \emph{role use} visualization.}
\label{lst:roleuse}
\end{figure}
\vspace{-3pt}
A frequent question is, what a given role does and which information is needed for those functions represented by the entity types connected to those functions.
This question is visually answered by the \enquote{role use} feature, which arranges roles, functions and entity types in concentric circles:
(1) The first ring consists of the given role and all roles that are connected by a path of \aurl{rdfs}{subClassOf} and \aurl{skos}{closeMatch} edges.
(2) The second ring consists of all functions adjacent to roles in the inner ring.
(3) The third ring consists of all entity types adjacent to functions in the middle ring.
(4) The final ring consists of all entity types that are connected to entity types from the third ring by a path of \aurl{skos}{closeMatch} and reverse \aurl{rdfs}{subClassOf} edges.
\cref{fig:classuse}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.6\linewidth]{class-use-project-manager.pdf}
    \caption{\emph{Role Use} of \aurl{bb}{ProjectManager}. Outermost layer ommitted due to space limitiations.}\label{fig:classuse}

\end{figure}

@@

\subsection*{Mixed Operations}
\subsubsection*{Spiderworm}
A \emph{spiderworm} is a path from node \emph{A} to node \emph{B} combined with a \emph{star} of \emph{B}.
\Cref{fig:spiderworm} shows how we use a spiderworm to teach a student how the new concept \enquote{quality of data} is connected the the already introduced concept \enquote{patient identification number.}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\linewidth]{spiderworm.pdf}
    \caption{\emph{Spiderworm} from \aurl{bb}{PatientIdentificationNumber} to \aurl{bb}{QualityOfData}~\cite{snikgraphposter}.}
	\label{fig:spiderworm}
\end{figure}
\vspace{-3pt}

@@

\begin{table}[h]
\centering
\caption{Namespaces.}
\label{tab:namespaces}
\begin{tabularx}{\linewidth}{|l|X|l|}
%\toprule
\hline
\textbf{Prefix}	&\textbf{Ontology}				&\textbf{Source}\\
%\midrule
meta	&\url{http://www.snik.eu/ontology/meta}		&Meta Model\\ \hline
bb		&\url{http://www.snik.eu/ontology/bb}		&Textbook~\cite{bb}\\\hline
ob		&\url{http://www.snik.eu/ontology/ob}		&Textbook~\cite{ob}\\\hline
%\url{http://www.snik.eu/ontology/he}		&Textbook~\cite{he}\\\hline
%\url{http://www.snik.eu/ontology/ciox}		&CIO Interview\\\hline
%\url{http://www.snik.eu/ontology/it4it}		&Standard~\cite{it4it}\\\hline
%k\bottomrule
\end{tabularx}
\end{table}

@@

@@

\section*{Acknowledgement}
This work is supported by the DFG (German Research Foundation) under the Project SNIK, Grant no. 1605/7-1 and 1387/8-1. SNIK Graph is presented in poster form at \cite{snikgraphposter}.
\section*{References}
